\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Page setup
\geometry{
    a4paper,
    left=1.5cm,
    right=1.5cm,
    top=1.5cm,
    bottom=1.5cm
}

% Colors
\definecolor{primarycolor}{RGB}{44,62,80}
\definecolor{secondarycolor}{RGB}{52,152,219}
\definecolor{accentcolor}{RGB}{231,76,60}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=secondarycolor,
    urlcolor=secondarycolor,
    pdfauthor={Tran Quoc Hung},
    pdftitle={CV - Tran Quoc Hung}
}

% Section formatting
\titleformat{\section}
    {\Large\bfseries\color{primarycolor}}
    {}
    {0em}
    {}
    [\titlerule]

\titleformat{\subsection}
    {\large\bfseries\color{secondarycolor}}
    {}
    {0em}
    {}

% Custom commands
\newcommand{\cvitem}[2]{
    \textbf{#1:} #2
}

% Remove page numbers
\pagestyle{empty}

\begin{document}

% =============== HEADER ===============
\begin{center}
    {\Huge\bfseries\color{primarycolor} TRAN QUOC HUNG}
    
    \vspace{0.3cm}
    
    {\Large\itshape 4th Year Student - Information Technology}
    
    \vspace{0.4cm}
    
    \begin{tabular}{c c c c}
        \faIcon{envelope} \href{mailto:hungtran2003lucky@gmail.com}{hungtran2003lucky@gmail.com} &
        \faIcon{phone} 091912124 &
        \faIcon{github} \href{https://github.com/Tiiadun123}{github.com/Tiiadun123} &
        \faIcon{university} HCMUE
    \end{tabular}
\end{center}

\vspace{0.5cm}

% =============== ABOUT ME ===============
\section*{\faIcon{user} About Me}
4th year student in Information Technology at Ho Chi Minh City University of Education. Passionate about full-stack web development and always eager to learn new technologies. I am a responsible, problem-solving focused individual who enjoys teamwork and collaboration.

\vspace{0.3cm}

% =============== SKILLS ===============
\section*{\faIcon{briefcase} Skills}

\begin{tabularx}{\textwidth}{X X}
    \subsection*{Frontend} &
    \subsection*{Backend} \\
    \begin{itemize}[leftmargin=*, itemsep=1pt]
        \item \textbf{ReactJs} - Build dynamic UIs
        \item HTML5 \& CSS3
        \item JavaScript ES6+
    \end{itemize} &
    \begin{itemize}[leftmargin=*, itemsep=1pt]
        \item \textbf{NodeJs} - Server-side dev
        \item Express.js
        \item RESTful API
        \item \textbf{Python} - General programming
    \end{itemize} \\
    
    \subsection*{Database} &
    \subsection*{Programming Concepts} \\
    \begin{itemize}[leftmargin=*, itemsep=1pt]
        \item \textbf{MySQL} - Relational database
        \item \textbf{SQL Server} - Database management
        \item \textbf{Supabase} - Backend as a Service
        \item SQL \& Queries
    \end{itemize} &
    \begin{itemize}[leftmargin=*, itemsep=1pt]
        \item \textbf{Object-Oriented Programming}
        \item Data Structures \& Algorithms
        \item Design Patterns
    \end{itemize} \\
\end{tabularx}

\subsection*{Tools \& Technologies}
\begin{itemize}[leftmargin=*, itemsep=1pt]
    \item Git \& GitHub
    \item VS Code
    \item Postman
\end{itemize}

\vspace{0.3cm}

% =============== EDUCATION ===============
\section*{\faIcon{graduation-cap} Education}

\begin{tabularx}{\textwidth}{X r}
    \textbf{\large Ho Chi Minh City University of Education (HCMUE)} & \colorbox{accentcolor}{\textcolor{white}{\textbf{2022 - 2026}}}
\end{tabularx}

\vspace{0.2cm}

\cvitem{Major}{Information Technology}

\cvitem{Status}{4th Year Student}

\vspace{0.3cm}

% =============== EXPERIENCE & OBJECTIVES ===============
\section*{\faIcon{lightbulb} Experience \& Objectives}

Currently a 4th year student actively \textbf{seeking internship or full-time opportunities} in web development. I have a solid foundation in ReactJs, NodeJs, and related technologies.

\vspace{0.2cm}

\textbf{My Goals:}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item[\color{secondarycolor}\checkmark] Gain practical experience in full-stack web application development
    \item[\color{secondarycolor}\checkmark] Learn and apply industry best practices and professional software development processes
    \item[\color{secondarycolor}\checkmark] Develop teamwork and communication skills in professional environments
    \item[\color{secondarycolor}\checkmark] Enhance understanding of application architecture and performance optimization
    \item[\color{secondarycolor}\checkmark] Master advanced programming concepts and technologies
\end{itemize}

\vspace{0.2cm}

\textbf{Ready to:} Learn new technologies, solve complex problems, and contribute value to the team.

\vspace{0.3cm}

% =============== PROJECTS ===============
\section*{\faIcon{folder} Projects}

Visit my \href{https://github.com/Tiiadun123}{\textbf{GitHub}} to see detailed projects and latest work.

\vspace{0.5cm}

% =============== FOOTER ===============
\begin{center}
    \small
    \textcolor{gray}{
        \textcopyright\ 2026 Tran Quoc Hung. All rights reserved. \\
        Last Updated: January 2026
    }
\end{center}

\end{document}